Enforced Invariant Confluence

### 2018-05-01 doc/paper/sections/introduction.tex
Added more on performance.

% TODO: add bit on performance.

In closing, here is an outline of the paper and of our contributions:
%
We propose a novel expression-oriented definition of \invariantconfluence{}
that is both formal and simple (\secref{InvariantConfluence}).
%
We develop an understanding of why \invariantclosure{} is not necessary for
\invariantconfluence{} and use this understanding to develop conditions under
which it is both necessary and sufficient (\secref{InvariantClosure}).
%
We exploit these conditions to design a general-purpose interactive decision
procedure for \invariantconfluence{} (\secref{InteractiveDecisionProcedure}).
%
We again exploit these conditions to design a novel non-trivial sufficient
condition for \invariantconfluence{}, called \mergereducibility.
%
We present segmented \invariantconfluence{}: a generalization of
\invariantconfluence{} that uses a small amount of coordination to maintain
invariants for replicated objects that are otherwise not \invariantconfluent{}
(\secref{SegmentedInvariantConfluence}).
%
We implement our decision procedures and sufficient conditions for both
\invariantconfluence{} and segmented \invariantconfluence{} in a system called
Lucy, then use Lucy to evaluate our methods (\secref{Evaluation}).

>>>>

Finally, we present Lucy: an implementation of our decision procedures and a
system for replicating \invariantconfluent{} and segmented
\invariantconfluent{} objects. Using Lucy, we find that our decision
procedures can efficiently handle a wide range of common workloads. For
example, in \secref{Evaluation}, we apply Lucy to foreign key constraints,
escrow transactions, an auction application, and the TPC-C benchmark. Lucy
processes these workloads in less than half a second, and no workload requires
more than 66 lines of code to specify. Moreover, we find that segmented
\invariantconfluent{} replication can achieve 100x to 10x more throughput than
linearizable replication for low-coordination workloads.

In closing, here is an outline of the paper and of our contributions:
%
We propose a novel expression-oriented definition of \invariantconfluence{}
that is both formal and simple (\secref{InvariantConfluence}).
%
We develop an understanding of why \invariantclosure{} is not necessary for
\invariantconfluence{} and use this understanding to develop conditions under
which it is both necessary and sufficient (\secref{InvariantClosure}).
%
We exploit these conditions to design a general-purpose interactive decision
procedure for \invariantconfluence{} (\secref{InteractiveDecisionProcedure}).
%
We again exploit these conditions to design a novel non-trivial sufficient
condition for \invariantconfluence{}, called \mergereducibility.
%
We present segmented \invariantconfluence{}: a generalization of
\invariantconfluence{} that uses a small amount of coordination to maintain
invariants for replicated objects that are otherwise not \invariantconfluent{}
(\secref{SegmentedInvariantConfluence}).
%
We evaluate our methods using a prototype implementation called Lucy
(\secref{Evaluation}).
